---
title: "CLIF Cohort Dashboard"
format: 
  dashboard:
    theme: custom.scss
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaflet)
library(htmltools)
library(knitr)

# Read site data and fix coordinates
sites <- read.csv("data/site_details.csv", stringsAsFactors = FALSE) %>%
  mutate(
    # Replace en dash with regular minus sign and convert to numeric
    Longitude = as.numeric(str_replace(Longitude, "−", "-")),
    Latitude = as.numeric(Latitude)
  )

# Read metrics data
metrics <- read.csv("data/metrics_data.csv", stringsAsFactors = FALSE)

# Create marker icons using Font Awesome
icons <- awesomeIconList(
  ready = makeAwesomeIcon(
    icon = "check",
    markerColor = "green",
    iconColor = "white",
    library = "fa"
  ),
  pending = makeAwesomeIcon(
    icon = "clock",
    markerColor = "orange",
    iconColor = "white",
    library = "fa"
  )
)

# Add icon type to the data
sites$icon_type <- ifelse(sites$Data.Ready == "Yes", "ready", "pending")

# Helper function to get metric value and format
get_metric_with_format <- function(metric_name) {
  metrics %>% 
    filter(Site == "Consortium Aggregate", Metric == metric_name) %>% 
    select(Value, Display_Format) %>% 
    head(1)
}

# Helper function to format numbers with commas
format_number <- function(value) {
  format(as.numeric(gsub("[^0-9]", "", value)), big.mark=",")
}

# Helper function to get metric value
get_metric <- function(metric_name) {
  metrics %>% 
    filter(Site == "Consortium Aggregate", Metric == metric_name) %>% 
    pull(Value)
}

# Helper function to format large numbers
format_large_number <- function(value) {
  format(as.numeric(gsub("[^0-9]", "", value)), big.mark=",")
}

# Helper function to format median [Q1,Q3] values
format_median_iqr <- function(metric_name, show_iqr = FALSE) {
  metric_data <- get_metric_with_format(metric_name)
  value <- metric_data$Value
  format <- metric_data$Display_Format
  
  if(is.na(value) || value == "") return("N/A")
  
  # Extract numbers using regex
  numbers <- str_extract_all(value, "\\d+\\.?\\d*")[[1]]
  if(length(numbers) >= 3) {
    median <- as.numeric(numbers[1])
    q1 <- as.numeric(numbers[2])
    q3 <- as.numeric(numbers[3])
    
    if(show_iqr) {
      return(sprintf("%.1f [%.1f, %.1f]", median, q1, q3))
    } else {
      return(sprintf("%.1f", median))
    }
  }
  return(value)
}

# Helper function to format n (%) values
format_percentage <- function(metric_name, show_n = FALSE) {
  metric_data <- get_metric_with_format(metric_name)
  value <- metric_data$Value
  format <- metric_data$Display_Format
  
  if(is.na(value) || value == "") return("N/A")
  
  # Extract numbers using regex
  n_match <- str_extract(value, "\\d+(?=\\s*\\()")  # Get number before parentheses
  pct_match <- str_extract(value, "\\d+\\.?\\d*(?=%\\))")  # Get percentage
  
  if(!is.na(pct_match)) {
    if(show_n && !is.na(n_match)) {
      return(sprintf("%s (%s%%)", format_large_number(n_match), pct_match))
    } else {
      return(sprintf("%s%%", pct_match))
    }
  }
  return(value)
}
```

# Home

## Row {.no-padding .g-0}
```{=html}
<style>
.no-padding {
  padding: 0 !important;
  margin: 0 !important;
}

.g-0 {
  --bs-gutter-x: 0 !important;
  --bs-gutter-y: 0 !important;
}

.top-stats {
  display: flex;
  flex-direction: row;
  gap: 1rem;
  width: 100vw;
  margin: 0;
  padding: 1rem;
  background: white;
  justify-content: space-between;
}

.stat-card {
  display: flex;
  flex-direction: column;
  align-items: center;
  padding: 1rem;
  background: transparent;
  border-radius: 4px;
  box-shadow: 0 1px 3px rgba(0,0,0,0.1);
  flex: 1;
  min-width: 120px;
}

.stat-icon {
  width: 24px;
  height: 24px;
  margin-bottom: 0.5rem;
  opacity: 0.7;
}

.stat-label {
  color: #983232;
  font-size: 0.8rem;
  opacity: 0.7;
  text-align: center;
  margin-bottom: 0.25rem;
  white-space: nowrap;
}

.stat-value {
  color: #983232;
  font-size: 1.5rem;
  font-weight: bold;
  text-align: center;
}

/* Tablet Styles */
@media screen and (max-width: 1024px) {
  .top-stats {
    flex-wrap: wrap;
    gap: 0.75rem;
  }
  
  .stat-card {
    flex: 1 1 calc(25% - 0.75rem);
    min-width: calc(25% - 0.75rem);
  }
}

/* Mobile Styles */
@media screen and (max-width: 768px) {
  .top-stats {
    gap: 0.35rem;
    padding: 0.5rem;
    width: 100%;
    justify-content: center;
  }
  
  .stat-card {
    flex: 0 1 calc(33.33% - 0.35rem);
    min-width: calc(33.33% - 0.35rem);
    padding: 0.5rem;
    margin-bottom: 0.35rem;
  }
  
  .stat-icon {
    width: 18px;
    height: 18px;
    margin-bottom: 0.25rem;
  }
  
  .stat-label {
    font-size: 0.7rem;
    line-height: 1.2;
    margin-bottom: 0.15rem;
  }
  
  .stat-value {
    font-size: 1.1rem;
    line-height: 1.2;
  }
}

/* Small Mobile Styles */
@media screen and (max-width: 480px) {
  .top-stats {
    padding: 0.35rem;
    gap: 0.25rem;
  }
  
  .stat-card {
    flex: 0 1 calc(50% - 0.25rem);
    min-width: calc(50% - 0.25rem);
    padding: 0.35rem;
    margin-bottom: 0.25rem;
  }
  
  .stat-icon {
    width: 16px;
    height: 16px;
    margin-bottom: 0.15rem;
  }
  
  .stat-label {
    font-size: 0.65rem;
    margin-bottom: 0.1rem;
  }
  
  .stat-value {
    font-size: 1rem;
  }
}

.stat-card.encounters {
  display: flex;
  flex-direction: column;
}

.encounters .number-container {
  display: flex;
  align-items: center;
  justify-content: center;
  gap: 0.5rem;
  order: 2;
}

.encounters .stat-icon {
  width: 1.5rem;
  height: 1.5rem;
  margin: 0;
}

.encounters .stat-label {
  order: 1;
}

.encounters .stat-value {
  margin: 0;
}

.stat-card.with-icon {
  display: flex;
  flex-direction: column;
}

.with-icon .value-container {
  display: flex;
  align-items: center;
  justify-content: flex-start;
  width: 100%;
}

.with-icon .stat-icon {
  margin-right: 0.5rem;
}

.with-icon .stat-value {
  flex: 1;
  text-align: left;
}

.stat-card.hospital {
  text-align: left;
  padding: 1rem;
}

.hospital .stat-label {
  text-align: left;
  margin-bottom: 0.5rem;
}

.hospital .value-row {
  display: flex;
  align-items: center;
  gap: 1rem;
}

.hospital .stat-icon {
  width: 2.5rem;
  height: 2.5rem;
}

.hospital .stat-value {
  text-align: left;
  font-size: 2rem;
}
</style>

<div class="top-stats">
  <div class="stat-card">
    <img src="icons/encounters.svg" class="stat-icon" alt="encounters">
    <div class="stat-label">Total ICU Encounters</div>
    <div class="stat-value">`r format_large_number(get_metric("N: ICU encounters"))`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/patients.svg" class="stat-icon" alt="patients">
    <div class="stat-label">Patients</div>
    <div class="stat-value">`r format_large_number(get_metric("N: Unique patients"))`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/years.svg" class="stat-icon" alt="years">
    <div class="stat-label">Years</div>
    <div class="stat-value">`r get_metric("Years")`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/hospitals.svg" class="stat-icon" alt="hospitals">
    <div class="stat-label">Hospitals</div>
    <div class="stat-value">`r format_large_number(get_metric("Hospitals "))`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/days.svg" class="stat-icon" alt="days">
    <div class="stat-label">Hospital Length of Stay (days)</div>
    <div class="stat-value">`r format_median_iqr("Total hospital days, median [Q1,Q3]")`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/sex.svg" class="stat-icon" alt="female">
    <div class="stat-label">Female</div>
    <div class="stat-value">`r format_percentage("Sex n (%): Female")`</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/race.svg" class="stat-icon" alt="race">
    <div class="stat-label">White</div>
    <div class="stat-value">61.5%</div>
  </div>
  
  <div class="stat-card">
    <img src="icons/hispanic.svg" class="stat-icon" alt="hispanic">
    <div class="stat-label">Hispanic</div>
    <div class="stat-value">`r format_percentage("Ethnicity n (%): Hispanic")`</div>
  </div>

  <div class="stat-card">
    <img src="icons/mortality.svg" class="stat-icon" alt="hispanic">
    <div class="stat-label">Mortality</div>
    <div class="stat-value">`r format_percentage("Hospital mortality n (%)")`</div>
  </div>

  <div class="stat-card">
    <img src="icons/sofa.svg" class="stat-icon" alt="sofa">
    <div class="stat-label">SOFA Median</div>
    <div class="stat-value">`r format_median_iqr("SOFA-97 TOTAL, median [Q1,Q3]")`</div>
  </div>
</div>
```

## Row {.mt-3}
### Map {width=70%}
```{r map}
#| out.width: "100%"
#| out.height: "500px"

leaflet(sites) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(lng = -98.5795, lat = 39.8283, zoom = 4) %>%
  addAwesomeMarkers(
    ~Longitude, ~Latitude,
    icon = ~icons[icon_type],
    popup = ~paste0(
      "<b>", Site, "</b><br>",
      "Location: ", `City..State.Province`, "<br>",
      "Hospitals: ", `Hospitals`, "<br>",
      "Total ICU Encounters: ", `Encounters`, "<br>",
      "Total Patients: ", `Patients`, "<br>",
      "Status: ", if_else(Data.Ready == "Yes", 
                         "<span style='color: green;'>Ready</span>", 
                         "<span style='color: orange;'>Pending</span>")
                   
    ),
    label = ~Site,
    clusterOptions = markerClusterOptions()
  ) %>%
  addLegend(
    position = "bottomright",
    colors = c("#4DAF4A", "#FF7F00"),
    labels = c("Ready", "Pending"),
    title = "Site Status"
  )
```

### Details {.tabset width=30%}

#### IMV Encounters
::: {.mb-8}
<div class="stat-card" style="margin-bottom: 1rem; background: transparent;">
  <img src="icons/vent.svg" alt="vasopressor" style="width: 90px; height: 64px;">
  <div class="stat-value" style="margin-bottom: 1rem;">`r format_percentage("IMV encounters n (%)")`</div>
  <div class="stat-label" >Encounters received mechanical ventilation</div>
</div>

<div style="height: auto; margin-top: 1rem;">
```{r imv-locations}
library(plotly)

# Create data frame for the chart
locations <- data.frame(
  Location = c("ICU", "ED", "Procedural", "Ward", "Other"),
  Count = c(230002, 42526, 16986, 12999, 4154),
  Percentage = c(75.0, 13.9, 5.5, 4.2, 1.4)
)

# Create custom color palette - adjusted to match image
colors <- c("#983232", "#B25959", "#CC8080", "#E6A6A6", "#FFD9D9")

# Create the donut chart
plot_ly(locations, labels = ~Location, values = ~Percentage, type = 'pie',
        hole = 0.6,
        marker = list(colors = colors),
        textposition = 'outside',
        textinfo = 'label+percent',
        hovertemplate = paste0(
          "%{label}<br>",
          "Count: %{customdata:,.0f}<br>",
          "Percentage: %{percent}<br>",
          "<extra></extra>"
        ),
        customdata = ~Count) %>%
  layout(
    showlegend = FALSE,
    title = list(
      text = "First Location of Intubation",
      y = 0.95,
      x = 0.5,
      xanchor = 'center',
      yanchor = 'top',
      font = list(
        color = '#983232',
        size = 16,
        family = "Inter"
      )
    ),
    paper_bgcolor = 'rgba(0,0,0,0)',
    plot_bgcolor = 'rgba(0,0,0,0)',
    margin = list(t = 60, l = 20, r = 20, b = 20),
    autosize = TRUE,
    # Make it a semi-circle
    polar = list(
      sector = c(0, 180)
    ),
    # Adjust the chart domain to show full semi-circle
    xaxis = list(domain = c(0.1, 0.9)),
    yaxis = list(domain = c(0, 0.95))
  )
```
</div>
:::

#### Ventilator Settings {.tabset}

##### Initial Mode of Ventilation

```{r vent-modes}
library(plotly)

# Create data frame for ventilation modes
vent_modes <- data.frame(
  Mode = c("Assist Control-Volume Control", 
           "Pressure-Regulated Volume Control",
           "SIMV",
           "Pressure support/CPAP",
           "Pressure Control",
           "Volume Support",
           "Other"),
  Count = c(183708, 39011, 32647, 21700, 7851, 79, 22046),
  Percentage = c(59.9, 12.7, 10.6, 7.1, 2.5, 0.0, 7.2)
)

# Sort by percentage in descending order
vent_modes <- vent_modes[order(-vent_modes$Percentage),]

# Create a color palette - using more distinct shades
colors <- c('#983232', '#CC8080', '#E6A6A6', '#B25959', '#FFB3B3', '#FFCCCC', '#FFE6E6')

# Create the vertical bar plot
plot_ly() %>%
  add_trace(
    data = vent_modes,
    x = ~seq_along(Mode),
    y = ~Percentage,
    type = 'bar',
    name = ~Mode,
    marker = list(color = colors),
    text = ~paste0(sprintf("%.1f", Percentage), "%"),
    textposition = 'outside',
    hovertemplate = paste0(
      "<b>%{data.name}</b><br>",
      "Count: %{customdata:,.0f}<br>",
      "Percentage: %{y:.1f}%<br>",
      "<extra></extra>"
    ),
    customdata = ~Count
  ) %>%
  layout(
    title = list(
      text = "Initial Mode of Ventilation",
      font = list(
        color = '#983232',
        size = 16,
        family = "Inter"
      ),
      y = 0.95
    ),
    yaxis = list(
      title = "Percentage of Encounters (%)",
      showgrid = TRUE,
      gridcolor = '#E5E5E5',
      zeroline = FALSE,
      range = c(0, max(vent_modes$Percentage) * 1.2)
    ),
    xaxis = list(
      title = "",
      showticklabels = FALSE,
      showgrid = FALSE
    ),
    paper_bgcolor = 'rgba(0,0,0,0)',
    plot_bgcolor = 'rgba(0,0,0,0)',
    margin = list(l = 50, r = 20, t = 50, b = 100),
    legend = list(
      orientation = "h",
      xanchor = "center",
      x = 0.5,
      y = -0.2,
      yanchor = "top",
      bgcolor = 'rgba(255, 255, 255, 0.9)',
      bordercolor = 'rgba(152, 50, 50, 0.2)',
      borderwidth = 1,
      font = list(size = 11),
      traceorder = "normal"
    ),
    showlegend = TRUE,
    font = list(family = "Inter"),
    bargap = 0.4,
    height = 400,
    autosize = TRUE
  )
```

##### Initial Settings

```{r vent-settings-table}
library(knitr)
library(kableExtra)

# Create data frame for ventilator settings
vent_settings <- data.frame(
  Setting = c("FiO2", "PEEP", "Respiratory rate", "Tidal Volume"),
  `Median [IQR]` = c(
    "0.4 [0.3,0.6]",
    "5.0 [5.0,8.0]",
    "16.0 [12.0,21.0]",
    "450.0 [380.0,500.0]"
  )
)

kable(vent_settings, 
      format = "html",
      escape = FALSE,
      align = c("l", "l"),
      col.names = c("Setting", "Median [IQR]")) %>%
  kable_styling(bootstrap_options = "condensed",
                full_width = TRUE,
                position = "left",
                font_size = 14) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(seq(1,4,2), background = "#f8f9fa")
```

<div style="color: #666; font-size: 0.8rem; margin-top: 1rem;">
Units: FiO2 (fraction), PEEP (cmH2O), Respiratory rate (breaths/min), Tidal Volume (mL)
</div>

#### Vasopressors

::: {.mb-5}
<div class="stat-card" style="margin-bottom: 2rem; background: transparent;">
  <img src="icons/vasopressors.svg" alt="vasopressor" style="width: 64px; height: 64px;">
  <div class="stat-value">`r format_percentage("Vasopressor encounters n (%)")`</div>
  <div class="stat-label">Encounters received Vasopressors</div>
</div>

```{r vasopressor-table}
library(knitr)
library(kableExtra)

# Create data frame directly with just the medications and their values
vasopressor_data <- data.frame(
  Medication = c("Phenylephrine", "Norepinephrine", "Vasopressin", "Angiotensin", 
                "Dopamine", "Epinephrine"),
  `Median [IQR]` = c(
    get_metric("Phenylephrine dose, median [Q1,Q3]"),
    get_metric("Norepinephrine dose, median [Q1,Q3]"),
    get_metric("Vasopressin dose, median [Q1,Q3]"),
    get_metric("Angiotensin dose, median [Q1,Q3]"),
    get_metric("Dopamine dose, median [Q1,Q3]"),
    get_metric("Epinephrine dose, median [Q1,Q3]")
  )
)

kable(vasopressor_data, 
      format = "html",
      escape = FALSE,
      align = c("l", "l"),
      col.names = c("Medication", "Median [IQR]")) %>%
  kable_styling(bootstrap_options = "condensed",
                full_width = FALSE,
                position = "left",
                font_size = 13) %>%
  column_spec(1, width = "150px") %>%
  column_spec(2, width = "150px") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(seq(1,6,2), background = "#f8f9fa")
```

<div style="color: #666; font-size: 0.8rem; margin-top: 1rem;">
The unit of measurement for all medications presented here is mcg/kg/min, except vasopressin, for which we use units/min
</div>
:::

# Data

```{r site-data-table}
#| warning: false
library(DT)

# Read the full dataset
site_data <- read.csv("data/final_website_data.csv", check.names = FALSE)

# Create an interactive table
datatable(site_data,
          options = list(
            pageLength = 15,
            scrollX = TRUE,
            dom = 'Bfrtip',
            buttons = c('copy', 'csv', 'excel'),
            initComplete = JS(
              "function(settings, json) {",
              "$(this.api().table().header()).css({'background-color': '#f8f9fa', 'color': '#983232'});",
              "}"
            )
          ),
          class = 'cell-border stripe',
          rownames = FALSE,
          filter = 'top',
          extensions = c('Buttons', 'FixedHeader'),
          style = 'bootstrap') %>%
  formatStyle(names(site_data),
             backgroundColor = '#ffffff',
             borderBottom = '1px solid #ddd')
```

The table above shows the complete dataset used to construct this dashboard. Currently there are eleven health systems within the CLIF consortium. We also have a pipeline from MIMIC-IV to CLIF. The distribution of MIMIC'ed CLIF is also represented above.
