---
title: "CLIF Cohort Dashboard"
format: 
  dashboard:
    theme: custom.scss
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaflet)
library(htmltools)

# Read site data and fix coordinates
sites <- read.csv("data/site_details.csv", stringsAsFactors = FALSE) %>%
  mutate(
    # Replace en dash with regular minus sign and convert to numeric
    Longitude = as.numeric(str_replace(Longitude, "−", "-")),
    Latitude = as.numeric(Latitude)
  )

# Create marker icons using Font Awesome
icons <- awesomeIconList(
  ready = makeAwesomeIcon(
    icon = "check",
    markerColor = "green",
    iconColor = "white",
    library = "fa"
  ),
  pending = makeAwesomeIcon(
    icon = "clock",
    markerColor = "orange",
    iconColor = "white",
    library = "fa"
  )
)

# Add icon type to the data
sites$icon_type <- ifelse(sites$Data.Ready == "Yes", "ready", "pending")
```

# Home {orientation="columns"}

## Left Column {width=55%}
### Row {height=50%}
#### Map
::: {.card}
```{r map}
#| out.width: "100%"
#| out.height: "400px"

# Create the map
leaflet(sites) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%  # Use a clean map style
  setView(lng = -98.5795, lat = 39.8283, zoom = 4) %>%  # Center on US
  addAwesomeMarkers(
    ~Longitude, ~Latitude,
    icon = ~icons[icon_type],
    popup = ~paste0(
      "<b>", Site, "</b><br>",
      "Location: ", `City..State.Province`, "<br>",
      "Status: ", if_else(Data.Ready == "Yes", 
                         "<span style='color: green;'>Ready</span>", 
                         "<span style='color: orange;'>Pending</span>")
    ),
    label = ~Site,
    clusterOptions = markerClusterOptions()  # Add clustering for overlapping markers
  ) %>%
  addLegend(
    position = "bottomright",
    colors = c("#4DAF4A", "#FF7F00"),  # Green and orange colors
    labels = c("Ready", "Pending"),
    title = "Site Status"
  )
```
:::

### Row {height=50%}
#### IMV Details
::: {.card}
::: {.card-header}
IMV Details
:::
::: {.card-body}
::: {.grid}
::: {.g-col-4}
##### Total IMV encounters
Location of intubation
:::
::: {.g-col-4}
##### Total IMV encounters
Initial mode
:::
::: {.g-col-4}
##### Ventilator settings
[Settings details]
:::
:::
:::
:::

## Right Column {width=45%}
### Overview
::: {.card}
::: {.card-header}
Overview
:::
::: {.card-body}
::: {.grid}
::: {.g-col-4}
#### Total encounters
[Value]
:::
::: {.g-col-4}
#### Total patients
[Value]
:::
::: {.g-col-4}
#### Years
[Value]
:::
:::

::: {.grid .mt-3}
::: {.g-col-6}
#### Hospitals
[Value]
:::
::: {.g-col-6}
#### Hospital Day
[Value]
:::
:::
:::
:::

### Demographics
::: {.card}
::: {.card-header}
Demographics
:::
::: {.card-body}
::: {.grid}
::: {.g-col-4}
#### Female
[Percentage]
:::
::: {.g-col-4}
#### Race
[Distribution]
:::
::: {.g-col-4}
#### Hispanic
[Percentage]
:::
:::
:::
:::

### Clinical Outcomes
::: {.card}
::: {.card-header}
Clinical Outcomes
:::
::: {.card-body}
::: {.grid}
::: {.g-col-3}
#### Mortality
[Metrics]
:::
::: {.g-col-3}
#### SOFA
[Scores]
:::
::: {.g-col-6}
#### Vasopressor details
[Details]
:::
:::
:::
:::

# Site Details
[This page will show when a specific site is selected]

# About
[Information about the CLIF cohort study]
